### 2021-07-21 paper/paper.tex
change title (preliminary)

\begin{itemize}
  \item Basic design of \trixi and its capabilities
  \item PID comparison of Fluxo and \trixi
  \item Discussion: Julia for numerical simulation science
  \item Prepare repro repo including scripts for \trixi and Fluxo
  \item Cite \cite{bezanson2017julia,schlottkelakemper2021purely,rackauckas2017differentialequations,revels2016forward,ranocha2021sbp}
  \item Change title to something like ``Adaptive high-order numerical simulations
  of hyperbolic PDEs with \trixi: A case study of Julia for scientific computing''?
  \item Restructure non-conservative stuff and add MHD benchmarks?
\end{itemize}

>>>>

\begin{itemize}
  \item Basic design of \trixi and its capabilities
  \item PID comparison of Fluxo and \trixi
  \item Discussion: Julia for numerical simulation science
  \item Prepare repro repo including scripts for \trixi and Fluxo
  \item Cite \cite{bezanson2017julia,schlottkelakemper2021purely,rackauckas2017differentialequations,revels2016forward,ranocha2021sbp}
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks?
\end{itemize}
